\bf A Unitary RG-based Auxiliary Model Approach to Strongly-Correlated Electronic Systems

### 2023-07-27 TilingProjectDraft/tilingProject.tex
finalised entanglement measures and computed rc2 - rc1

\subsection{\(k-\)space mutual information}
Another measure of many-body correlations would be the mutual information between two momentum-space states. The mutual information \(I_2\) between the states \(\ket{\vec k, \sigma}\) and \(\ket{\vec q, \sigma}\) is defined as
\begin{equation}\begin{aligned}
	I_2(\vec k\sigma:\vec q\sigma) = S_\text{EE}(\rho_{\vec k\sigma}) + S_\text{EE}(\rho_{\vec q\sigma}) - S_\text{EE}(\rho_{\vec k\sigma, \vec q\sigma})~,
\end{aligned}\end{equation}
where \(S_\text{EE}(\rho)\) is the von-Neumann entropy associated with the density matrix \(\rho\). The reduced density matrices \(\rho_{\vec k\sigma}\) and \(\rho_{\vec q\sigma}\) can be computed using eq.~\ref{density_matrix_kspace}; the reduced density matrix \(\rho_{\vec q\sigma, \vec k\sigma}\) has both the states \(\vec k\sigma\) and \(\vec q\sigma\) traced out, and it can be obtained by substituting \(\rho_{\vec k\sigma}\) back into eq.~\ref{density_matrix_kspace}:
\begin{equation}\begin{aligned}
	&\rho_{\vec k\sigma, \vec q\sigma} \\
	=& \hat n_{\vec q\sigma}\rho_{\vec k\sigma}\hat n_{\vec q\sigma} + \hat h_{\vec q\sigma}\rho_{\vec k\sigma}\hat h_{\vec q\sigma}\\
	=& \left[\hat n_{d,\sigma} + \hat n_{z,\sigma} + \frac{\xi_{\vec q}}{\sqrt \mathcal{W}}\left(c^\dagger_{d,\sigma}c_{z,\sigma} + \text{h.c.} \right)\right] \rho_{\vec k\sigma} \left[\hat n_{d,\sigma} + \hat n_{z,\sigma} + \frac{\xi_{\vec q}}{\sqrt \mathcal{W}}\left(c^\dagger_{d,\sigma}c_{z,\sigma} + \text{h.c.} \right)\right]\\
				  &+ \left[\hat h_{d,\sigma} + \hat h_{z,\sigma} + \frac{\xi_{\vec q}}{\sqrt \mathcal{W}}\left(c_{d,\sigma}c^\dagger_{z,\sigma} + \text{h.c.} \right)\right] \rho_{\vec k\sigma} \left[\hat h_{d,\sigma} + \hat h_{z,\sigma} + \frac{\xi_{\vec q}}{\sqrt \mathcal{W}}\left(c_{d,\sigma}c^\dagger_{z,\sigma} + \text{h.c.} \right)\right]\\
	=& \left[\left(\hat n_{d,\sigma} + \hat n_{z,\sigma}\right)^2 + \frac{\xi_{\vec q} + \xi_{\vec k}}{\sqrt \mathcal{W}}\left(c^\dagger_{d,\sigma}c_{z,\sigma} + \text{h.c.} \right)+ \frac{\xi_{\vec q} \xi_{\vec k}}{\mathcal{W}}\left( \hat n_{d\sigma} - \hat n_{0\sigma} \right)^2 \right] \rho_{\vec k\sigma} \times\\
	 &\left[\left(\hat n_{d,\sigma} + \hat n_{z,\sigma}\right)^2 + \frac{\xi_{\vec q} + \xi_{\vec k}}{\sqrt \mathcal{W}}\left(c^\dagger_{d,\sigma}c_{z,\sigma} + \text{h.c.} \right)+ \frac{\xi_{\vec q} \xi_{\vec k}}{\mathcal{W}}\left( \hat n_{d\sigma} - \hat n_{0\sigma} \right)^2 \right]\\
				  &+ \left[\hat h_{d,\sigma} + \hat h_{z,\sigma} + \frac{\xi_{\vec q}}{\sqrt \mathcal{W}}\left(c_{d,\sigma}c^\dagger_{z,\sigma} + \text{h.c.} \right)\right] \rho_{\vec k\sigma} \left[\hat h_{d,\sigma} + \hat h_{z,\sigma} + \frac{\xi_{\vec q}}{\sqrt \mathcal{W}}\left(c_{d,\sigma}c^\dagger_{z,\sigma} + \text{h.c.} \right)\right]
\end{aligned}\end{equation}

@@

\begin{figure}[!htb]
\includegraphics[width=\textwidth]{vne_kspace_all.pdf}
\caption{Momentum dependence of \(k-\)space von Neumann entanglement entropy \(S_\text{EE}(\vec k)\) and \(k-\)space mutual information \(I_2(\vec k:-\vec k)\). The first two frames (from the left) show the variation in entanglement of a \(k-\)space in the \(k_x\) direction as the transition parameter \(r\) is tuned through the metal-insulator transition, for two values of \(k_y\). The last two frames show the distribution of mutual information between two states \(\vec k\) and \(-\vec k\), in the \(k_x-k_y\) plane, for two values of \(r\). \(r/r_c=0.9\) represents a highly correlated metal, while \(r/r_c=1\) represents the non-Fermi liquid metal formed at the transition.}
\label{entanglement_kspace}
\end{figure}

>>>>

\subsection{\(k-\)space mutual information}
Another measure of many-body correlations would be the mutual information between two momentum-space states. The mutual information \(I_2\) between the states \(\ket{\vec k, \sigma}\) and \(\ket{\vec q, \sigma}\) is defined as
\begin{equation}\begin{aligned}
	I_2(\vec k\sigma:\vec q\sigma) = S_\text{EE}(\rho_{\vec k\sigma}) + S_\text{EE}(\rho_{\vec q\sigma}) - S_\text{EE}(\rho_{\vec k\sigma, \vec q\sigma})~,
\end{aligned}\end{equation}
where \(S_\text{EE}(\rho)\) is the von-Neumann entropy associated with the density matrix \(\rho\). The reduced density matrices \(\rho_{\vec k\sigma}\) and \(\rho_{\vec q\sigma}\) can be computed using eq.~\ref{density_matrix_kspace}; the reduced density matrix \(\rho_{\vec q\sigma, \vec k\sigma}\) has both the states \(\vec k\sigma\) and \(\vec q\sigma\) traced out, and it can be obtained by substituting \(\rho_{\vec k\sigma}\) back into eq.~\ref{density_matrix_kspace}:
\begin{equation}\begin{aligned}
	&\rho_{\vec k\sigma, \vec q\sigma} \\
	=& \hat n_{\vec q\sigma}\rho_{\vec k\sigma}\hat n_{\vec q\sigma} + \hat h_{\vec q\sigma}\rho_{\vec k\sigma}\hat h_{\vec q\sigma}\\
	=& \left[\hat n_{d,\sigma} + \hat n_{z,\sigma} + \frac{\xi_{\vec q}}{\sqrt \mathcal{W}}\left(c^\dagger_{d,\sigma}c_{z,\sigma} + \text{h.c.} \right)\right] \rho_{\vec k\sigma} \left[\hat n_{d,\sigma} + \hat n_{z,\sigma} + \frac{\xi_{\vec q}}{\sqrt \mathcal{W}}\left(c^\dagger_{d,\sigma}c_{z,\sigma} + \text{h.c.} \right)\right]\\
				  &+ \left[\hat h_{d,\sigma} + \hat h_{z,\sigma} + \frac{\xi_{\vec q}}{\sqrt \mathcal{W}}\left(c_{d,\sigma}c^\dagger_{z,\sigma} + \text{h.c.} \right)\right] \rho_{\vec k\sigma} \left[\hat h_{d,\sigma} + \hat h_{z,\sigma} + \frac{\xi_{\vec q}}{\sqrt \mathcal{W}}\left(c_{d,\sigma}c^\dagger_{z,\sigma} + \text{h.c.} \right)\right]
\end{aligned}\end{equation}

@@

\begin{figure}[!htb]
\includegraphics[width=\textwidth]{vne_kspace_all.pdf}
\caption{Momentum dependence of \(k-\)space von Neumann entanglement entropy \(S_\text{EE}(\vec k)\). The four frames (from the left) show the variation in entanglement of a \(k-\)space in the \(k_x-k_y\) plane as the transition parameter \(r\) is tuned through the metal-insulator transition. \(r/r_c=0.5\) represents a very weakly correlated metal, \(r/r_c=0.8,0.9\) represents a highly correlated metal in the Kondo phase of the auxiliary model, and \(r/r_c \sim 1\) represents the non-Fermi liquid metal formed at the transition.}
\label{entanglement_kspace}
\end{figure}

\begin{figure}[!htb]
\includegraphics[width=\textwidth]{mutinfo_kspace_all.pdf}
\caption{Momentum dependence of \(k-\)space mutual information \(I_2(\vec k: -\vec k)\). The four frames (from the left) show the variation in entanglement between the \(\vec k\) and \(-\vec k\) states in the \(k_x-k_y\) plane as the transition parameter \(r\) is tuned through the metal-insulator transition. \(r/r_c=0.5\) represents a very weakly correlated metal, \(r/r_c=0.8,0.9\) represents a highly correlated metal in the Kondo phase of the auxiliary model, and \(r/r_c \sim 1\) represents the non-Fermi liquid metal formed at the transition.}
\label{mutinfo_kspace}
\end{figure}
